Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-11-18 appendices/appendixa.tex
summary
language options were not restored after processing dutch summary. I hope this fixes it

\chapter{Tutorial on setting up time-heterogeneous Epoch Models of substitution in BEAST.}

@@

Naturally we want to log the three parameters of our epoch model. 
To monitor the analysis we start with the screen log. 
Look for the following line: <{\color{darkblue}log} {\color{darkblue}id}="screenLog" {\color{darkblue}logEvery}="5000">.

@@

We then still need to modify the lines responsible for storing the parameter estimates of the epoch model to file.
Go to the beginning of the {\color{darkblue}log} block responsible for keeping a log file, i.e. <{\color{darkblue}log} {\color{darkblue}id}="fileLog" {\color{darkblue}logEvery}="1000">.
Find the line which references the \textit{kappa} parameter and paste there instead:

>>>>

\chapter{Tutorial on setting up time-heterogeneous Epoch Models of substitution in BEAST.\label{app:epoch}}
\chaptermark{Epoch Models of substitution in BEAST}

@@

Naturally we want to log the three parameters of our epoch model. 
To monitor the analysis we start with the screen log. 
Look for the following line: <{\color{darkblue}log} {\color{darkblue}id}=\textquotedbl{}screenLog \textquotedbl{}{\color{darkblue}logEvery}=\textquotedbl{}5000\textquotedbl{}>.

@@

We then still need to modify the lines responsible for storing the parameter estimates of the epoch model to file.
Go to the beginning of the {\color{darkblue}log} block responsible for keeping a log file, i.e. <{\color{darkblue}log} {\color{darkblue}id}=\textquotedbl{}fileLog\textquotedbl{} {\color{darkblue}logEvery}=\textquotedbl{}1000\textquotedbl{}>.
Find the line which references the \textit{kappa} parameter and paste there instead:
